Delta Smelt Enclosure Study 2019 Hybrid Paper Analysis

### 2022-10-18 smelt_2019_allseasons/Diet 2019.Rmd
moving over files I had in a seperate folder for diet and zoop, removing old diet code

---
title: "2019 Diet Data"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

@@

# bring in contractor (UW) data
```{r}
diet2 <- read_csv('smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv') #new data, not edited at all

@@

@@

#change location titles 
diet$Location[diet$Location =="RIVERS"] <- "RV.Feb"
diet$Location[diet$Location =="Sac DWSC"] <- "DWSC.Apr"
diet$Location[diet$Location =="SM"] <- "SM.Nov"
diet$Location[diet$Location =="YB"] <- "YB.Nov"
#RV a little trickier with two dates
diet$ld = paste(diet$Location, diet$Date)
diet$Location[diet$ld =="RV 8/28/2019"] <- "RV.Aug"
diet$Location[diet$ld =="RV 11/6/2019"] <- "RV.Nov"
RV <- filter(diet, Location == "RV")
diet$Location[diet$ld =="RV 11/7/2019"] <- "RV.Nov"

@@

@@

# plot number of empty stomachs
## these will not be included in the 100% stacked bar later
```{r}
#order locations
stomach_abundance$Location <- stomach_abundance$Location.x
stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("RV.Feb", "DWSC.Apr", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

@@

#order locations
prop$Location <- ordered(prop$Location, levels = c("RV.Feb", "DWSC.Apr", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2", "#8C8C8C")
legend_title <- "Taxa"

>>>>

---
title: "Delta Smelt Enclosure Study 2019 Hybrid Paper Analysis"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

@@

# bring in contractor (UW) data
```{r}
diet2 <- read_csv("hybrid study/DSM Cage Diets 2019-2020.csv") #new data, not edited at all

diet2$Date <- mdy(diet2$Date)

@@

str(diet2)

@@

#change location titles 
diet$Location[diet$Location =="RIVERS"] <- "RV.Feb"
diet$Location[diet$Location =="Sac DWSC"] <- "DWSC.Apr"
diet$Location[diet$Location =="SM"] <- "SM.Nov"
diet$Location[diet$Location =="YB"] <- "YB.Nov"
#RV a little trickier with two dates
diet$ld = paste(diet$Location, diet$Date)
diet$Location[diet$ld =="RV 2019-08-28"] <- "RV.Aug"
diet$Location[diet$ld =="RV 2019-11-06"] <- "RV.Nov"
RV <- filter(diet, Location == "RV")
diet$Location[diet$ld =="RV 2019-11-07"] <- "RV.Nov"

@@

#remove DWSC
diet<-diet[diet$Location != "DWSC.Apr",]

@@

# plot number of empty stomachs
## these will not be included in the 100% stacked bar later
```{r}
#order locations
stomach_abundance$Location <- stomach_abundance$Location.x
stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

@@

#order locations
prop$Location <- ordered(prop$Location, levels = c("RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2")
legend_title <- "Taxa"
